Short-term hourly forecasting for care services

### 2021-10-07 paper/paper.Rmd
Plot code in rmd

---
title: Short-term hourly forecasting for care services
author:
  - name: Author1
    email: email1@example.com
    affiliation: University1
    footnote: 1
  - name: Author2
    email: email2@example.com
    affiliation: University2
    footnote: 2
  - name: Ivan Svetunkov
    email: i.svetunkov@lancaster.ac.uk
    affiliation: Centre for Marketing Analytics and Forecasting, Lancaster University, UK
    footnote: 2
address:
  - code: University1
    address: Cardiff business school, 3 Colum Drive, CF10 3EU, Cardiff
  - code: University2
    address: adress2
  - code: University3
    address: adress3
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"

@@

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
```

@@

If we assume that our predictive distribution follows a given parametric distribution, the forecasting task becomes ones of predicting the future values of that distribution's parameters. Generalised additive models for location, scale and shape (GAMLSS) are distributional regression models where the parameters of the assumed distribution may be modelled as additive functions of explanatory variables. This provides a powerful and flexible framework for probabilistic forecasting, provided that a suitable distribution and additive structures can be found. In practice, this means experimenting with various distributions and evaluating their suitability using available training data.

@@

```{r fig-quantilebias}
## Should reduce the number of models shown here... it's really hard to tell them appart!
knitr::include_graphics(rep("../results/QuantileBias.png"))
```

@@

```{r fig-skill}
knitr::include_graphics(rep("../results/Skill_rel2bench_reduced.png"))
```

>>>>

---
title: Short-term hourly forecasting for care services
author:
  - name: Author1
    email: email1@example.com
    affiliation: University1
    footnote: 1
  - name: Jethro Browell
    email: jethro.browell@glasgow.ac.uk
    affiliation: School of Mathematics and Statistics, University of Glasgow, UK
    footnote: 2
  - name: Ivan Svetunkov
    email: i.svetunkov@lancaster.ac.uk
    affiliation: Centre for Marketing Analytics and Forecasting, Lancaster University, UK
    footnote: 2
address:
  - code: University1
    address: Cardiff business school, 3 Colum Drive, CF10 3EU, Cardiff
  - code: University2
    address: adress2
  - code: University3
    address: adress3
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"

@@

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggplot2)
library(ggthemes)
library(data.table)
library(RColorBrewer)
```

@@

If we assume that our predictive distribution follows a given parametric distribution, the forecasting task becomes ones of predicting the future values of that distribution's parameters. Generalised Additive Models for Location, Scale and Shape (GAMLSS) are distributional regression models where the parameters of the assumed distribution may be modelled as additive functions of explanatory variables. This provides a powerful and flexible framework for probabilistic forecasting, provided that a suitable distribution and additive structures can be found. In practice, this means experimenting with various distributions and evaluating their suitability using available training data.

@@

```{r fig-quantilebias}
## Should reduce the number of models shown here... it's really hard to tell them appart!
# knitr::include_graphics(rep("../results/QuantileBias.png"))

load("../results/all_results_paper_2021-10-07.Rda")

REL_nom <- data.table(Nominal=seq(0,1,by=0.05),
                      Empirical=seq(0,1,by=0.05),
                      `Quantile Bias`= 0,
                      Method="Nominal")

REL[,`Quantile Bias`:=Empirical-Nominal]

ggplot(data=REL[Horizon=="All" & Issue == "All",],aes(x=Nominal,y=`Quantile Bias`,group=Method,color=Method)) +
  geom_line(data=REL_nom,aes(x=Nominal,y=`Quantile Bias`), color="black",size=1.1,show.legend = F) +
  geom_line() + geom_point() +
  xlim(c(0,1)) + ylim(c(-0.2,0.2)) + #ggtitle("Quantile Bias") +
  theme_few()

@@

```{r fig-skill}
# knitr::include_graphics(rep("../results/Skill_rel2bench_reduced.png"))

load("../results/all_results_paper_2021-10-07.Rda")

plotdata <- melt(bootdata[,100*(get(REF)-.SD)/get(REF),.SDcols=NAMES],
                 measure.vars =  1:length(NAMES),variable.name = "Method",
                 value.name = "Skill Score")

## Merge Reliability for colouring...
plotdata <- merge(plotdata,REL[kfold=="Test" & Horizon=="All" & Issue == "All",.(Qbias=mean(abs(Nominal-Empirical))),by="Method"],
                  by="Method",all.x = T)

ggplot(plotdata[`Skill Score`>-2,], aes(x=reorder(Method, -`Skill Score`), y=`Skill Score`, fill=Qbias)) + 
  ylab("Pinball Skill Score [%]") +
  geom_boxplot() + theme_few() +
  # ggtitle("Pinball Skill Score Relative to Benchmark 2") +
  theme(axis.text.x = element_text(angle = -80)) + #scale_fill_manual(values=cbPalette) +
  # scale_x_discrete(labels= paste0(substring(NAMES, 1,4),".")) +
  geom_hline(yintercept=0, linetype="dashed",size=0.5)+
  scale_fill_gradientn(colours = rev(brewer.pal(n = 11, name = "RdYlGn")),
                       limits=c(0,0.11))+
  labs(fill = "Quantile Bias",x="Method")
